Evaluating Variable Importances

### 2019-03-10 Scripts/evaluating_variable_importances.Rmd
editting script to fix axes

ggplot(vim.gm12878.RUS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

@@

ggplot(vim.K562.RUS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

@@

ggplot(vim.gm12878.ROS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

@@

ggplot(vim.K562.ROS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

@@

ggplot(vim.gm12878.none.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

@@

ggplot(vim.K562.none.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

>>>>

ggplot(vim.gm12878.RUS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient2(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Variable \n Importance",
                        limits = c(0,100),
                        breaks = c(0,25,50,75, 100),
                        labels = c("0", "25", "50", "75", "100")) +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation") +
    theme(#legend.position = c(.10, .10), 
        #legend.justification = c(.10, .10),
        #panel.border = element_rect(colour = "black", fill=NA),
        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20) #,
        #legend.background = element_rect(fill="white",
        #                                 size=0.5, 
        #                                 linetype="solid", 
        #                                 colour ="black")
        )

@@

ggplot(vim.K562.RUS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient2(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Variable \n Importance",
                        limits = c(0,100),
                        breaks = c(0,25,50,75, 100),
                        labels = c("0", "25", "50", "75", "100")) +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation") +
    theme(#legend.position = c(.10, .10), 
        #legend.justification = c(.10, .10),
        #panel.border = element_rect(colour = "black", fill=NA),
        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20) #,
        #legend.background = element_rect(fill="white",
        #                                 size=0.5, 
        #                                 linetype="solid", 
        #                                 colour ="black")
        )

@@

ggplot(vim.gm12878.ROS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient2(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Variable \n Importance",
                        limits = c(0,100),
                        breaks = c(0,25,50,75, 100),
                        labels = c("0", "25", "50", "75", "100")) +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation") +
    theme(#legend.position = c(.10, .10), 
        #legend.justification = c(.10, .10),
        #panel.border = element_rect(colour = "black", fill=NA),
        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20) #,
        #legend.background = element_rect(fill="white",
        #                                 size=0.5, 
        #                                 linetype="solid", 
        #                                 colour ="black")
        )

@@

ggplot(vim.K562.ROS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient2(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Variable \n Importance",
                        limits = c(0,100),
                        breaks = c(0,25,50,75, 100),
                        labels = c("0", "25", "50", "75", "100")) +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation") +
    theme(#legend.position = c(.10, .10), 
        #legend.justification = c(.10, .10),
        #panel.border = element_rect(colour = "black", fill=NA),
        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20) #,
        #legend.background = element_rect(fill="white",
        #                                 size=0.5, 
        #                                 linetype="solid", 
        #                                 colour ="black")
        )

@@

ggplot(vim.gm12878.none.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient2(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Variable \n Importance",
                        limits = c(0,100),
                        breaks = c(0,25,50,75, 100),
                        labels = c("0", "25", "50", "75", "100")) +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation") +
    theme(#legend.position = c(.10, .10), 
        #legend.justification = c(.10, .10),
        #panel.border = element_rect(colour = "black", fill=NA),
        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20) #,
        #legend.background = element_rect(fill="white",
        #                                 size=0.5, 
        #                                 linetype="solid", 
        #                                 colour ="black")
        )

@@

ggplot(vim.K562.none.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient2(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Variable \n Importance",
                        limits = c(0,100),
                        breaks = c(0,25,50,75, 100),
                        labels = c("0", "25", "50", "75", "100")) +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation") +
    theme(#legend.position = c(.10, .10), 
        #legend.justification = c(.10, .10),
        #panel.border = element_rect(colour = "black", fill=NA),
        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20) #,
        #legend.background = element_rect(fill="white",
        #                                 size=0.5, 
        #                                 linetype="solid", 
        #                                 colour ="black")
        )
